---
output: html_document
---

```{r, echo=FALSE}
# Define variable containing url
logoUrl <- "https://www.underconsideration.com/brandnew/archives/northeastern_university_logo.png"
```

<center><img src="`r logoUrl`" width="650" height="300"></center>

<br>
<p><center>
<font size = 6> ALY6010: Final Project</font> </center>
</p>

<style>
        .tab {
            display: inline-block;
            margin-left: 40px;
        }
        .tab1 {
            display: inline-block;
            margin-left: 50px;
        }
        .tab2 {
            display: inline-block;
            margin-left: 60px;
        }
        .tab3 {
            display: inline-block;
            margin-left: 70px;
        }
        .tab4 {
            display: inline-block;
            margin-left: 80px;
        }
        .tab5 {
            display: inline-block;
            margin-left: 100px;
        }
        table {
          table-layout: fixed ;
          width: 100% ;
        }
</style>

<br>
<p>
<font size = 4>
<br><b> Name     <span class="tab4"></span><span class="tab4"></span></b> : Jeseeka Shah, Sanjana Chaudhari and Supreeth Murugesh
<br><b> Instructor    <span class="tab4"></span><span class="tab"></span></b> : Prof. Amin Karimpour
<br><b> Class    <span class="tab5"></span><span class="tab2"></span></span></b> : Probability Theory and Introductory Statistics
<br><b> School   <span class="tab4"></span></b> <span class="tab2"></span> : Northeastern University - College of Professional Studies
<br><b> Date of submission <span class="tab"></span></b> : `r format(Sys.time(), "%d %B, %Y")` </font>
</p>


```{r warning=FALSE, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(plotrix)
library(plotly)
library(knitr)
library(kableExtra)
library(ggcorrplot)
```


<br><b><p>
<font size=5 color="#a84551">
Dataset 
</font>
</p></b>

```{r}
# Loading the dataset 
superstore_2011_2015 <- read.csv("Dataset/superstore-2011-2015.csv")

# Considering only the US market for Analysis 
superstore_2011_2015 <- filter(superstore_2011_2015,  superstore_2011_2015$Market == "US")

# Omitting NA values
superstore_2011_2015 <- na.omit(superstore_2011_2015)

# Calculating Total Sales
superstore_2011_2015 <- mutate(superstore_2011_2015, 
                               Total_Sales = superstore_2011_2015$Sales * superstore_2011_2015$Quantity)
```

<br><b><p>
<font size=5 color="#a84551">
Descriptive Statistics of numerical variables
</font>
</p></b>

```{r}
columnNames <- c('Sales', 'Discount', 'Profit', 'Shipping Cost', 'Total Sales')
rowNames <- c('Mean', 'Standard Deviation', 'Range', 'Median')

# Descriptive statistics of Discount 
meanDiscount <- round(mean(superstore_2011_2015$Discount),2)
stdDiscount <- round(sd(superstore_2011_2015$Discount),4)
rangeDiscount <- round(max(superstore_2011_2015$Discount) - min(superstore_2011_2015$Discount),2)
medianDiscount <- median(superstore_2011_2015$Discount)  

discountStats <- rbind(meanDiscount, stdDiscount, rangeDiscount, medianDiscount)

# Descriptive statistics of Sales
meanSales <- mean(superstore_2011_2015$Sales)
stdSales <- round(sd(superstore_2011_2015$Sales),2)
rangeSales <- max(superstore_2011_2015$Sales) - min(superstore_2011_2015$Sales)
medianSales <- median(superstore_2011_2015$Sales)

salesStats <- rbind(meanSales, stdSales, rangeSales, medianSales)

# Descriptive statistics of Profits
meanProfit <- mean(superstore_2011_2015$Profit)
stdProfit <- round(sd(superstore_2011_2015$Profit),2)
rangeProfit <- max(superstore_2011_2015$Profit) - min(superstore_2011_2015$Profit)
medianProfit <- median(superstore_2011_2015$Profit)

ProfitStats <- rbind(meanProfit, stdProfit, rangeProfit, medianProfit)

# Descriptive statistics of Shipping cost of the product
meanShippingCost <- mean(superstore_2011_2015$Shipping.Cost)
stdShippingCost <- round(sd(superstore_2011_2015$Shipping.Cost),2)
rangeShippingCost <- max(superstore_2011_2015$Shipping.Cost) - min(superstore_2011_2015$Shipping.Cost)
medianShippingCost <- median(superstore_2011_2015$Shipping.Cost)

ShippingCostStats <- rbind(meanShippingCost, stdShippingCost, rangeShippingCost, medianShippingCost)
combinedData <- cbind(discountStats, salesStats, ProfitStats, ShippingCostStats)

tableData <- combinedData
rownames(tableData) <- c('Mean', 'Standard Deviation', 'Range', 'Median')
colnames(tableData) <- c('Discount', 'Sales', 'Profit', 'Shipping Cost')
kable(tableData, caption = "<center><strong>Table 1: Statistics of 4 numerical variables</strong></center>", escape = FALSE,
    format = "html") %>% kable_material(c("striped", "hover"))
```

<br><b><p>
<font size=5 color="#a84551">
Exploratory Data analysis
</font>
</p></b>

```{r}
par(mar=c(5,8,4,2))
# Plot: Orders by each categories
colorname=RColorBrewer::brewer.pal(5,"Dark2") 
y= barplot(table(superstore_2011_2015$Category), 
                 ylim=c(0,8000), 
                 col = colorname, 
                 border="black", 
                 main = "Bar Plot for Category Count", 
                 xlab = "Category", 
                 ylab = "Freqency of Category Count", 
                 col.main="burlywood4", 
                 col.lab="burlywood4") 
```


```{r}
par(mar=c(5,8,4,2))
#Plot: Sales for different 
ggplot() + geom_jitter(data = superstore_2011_2015, 
                       aes(x = Region, y = Sales, fill = Region, colour=Region), 
                       stat = "identity") + 
  labs(x = "Region", y = "Sales ($)", title = "Sales Distribution in different regions", subtitle = "Dataset: Superstore Data") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme(plot.title = element_text(size=12, hjust=0.5, colour="black", vjust=-1)) +
  theme(plot.subtitle = element_text(size=9, hjust=0.5, colour="black", vjust=-1))
```


```{r warning=FALSE}
par(mar=c(5,8,4,2))
#Plot: Sales Vs. Profit with mean and Linear Regression

plot(superstore_2011_2015$Sales, y=superstore_2011_2015$Profit, 
     pch = 19, col = "orange", fit="lm", 
     xlab = "Sales ($)",
     ylab = "Profit ($)",
     main = "Sales vs Distribution")  
abline(h = mean(superstore_2011_2015$Profit), col = 'steelblue', lwd = 3, lty = 2)  
reg_model <- lm(Profit ~ Sales, data = superstore_2011_2015) 
abline(reg_model, col="purple")  
```


```{r}
par(mar=c(5,8,4,2))
# Plot: Profit made by catergories
superstore_2011_2015 %>% ggplot(aes(x = Category, y = Profit)) + 
         geom_point(aes(width = 0.9, outlier.shape = NA,color = Category)) +
  labs(title = "Profit distribution in Product categories", 
       subtitle = "Dataset: Superstore Data",
       color = "Category") +
  theme(plot.title = element_text(size=12, hjust=0.5, colour="black", vjust=-1)) +
  theme(plot.subtitle = element_text(size=9, hjust=0.5, colour="black", vjust=-1))
```

```{r}

```


```{r}
par(mar=c(5,8,4,2))
# Plot: Shipmode and Shipping cost
ggplot(superstore_2011_2015, 
       aes(x = Ship.Mode, 
           y = Shipping.Cost, 
           color = Ship.Mode)) + 
  geom_jitter(position=position_jitter(0.2), shape=17) +
  theme_minimal() + 
  labs(x="Shipmode", y="Shipping Cost($)", 
       title = "Shipping cost for different shipping modes", 
       subtitle = "Dataset: Superstore Data",
       color = "Shipping Mode") +
  theme(plot.title = element_text(size=12, hjust=0.5, colour="black", vjust=-1)) +
  theme(plot.subtitle = element_text(size=9, hjust=0.5, colour="black", vjust=-1)) + 
  scale_colour_manual(values=c("#AA2A64", "#BF403B", "#274530", "#779645")) +
  scale_shape_manual(values=c("#EDB361", "#BF403B", "#274530", "#779645")) 
```


```{r}
# Plot: Order count in each product category
par(mar=c(5,8,4,2))
categoryCount <- table(superstore_2011_2015$Category)
categoryCountPlot <- barplot(categoryCount, 
                              main = "Order count in each product category", 
                              ylab = "Count",
                              xlab = "Category",
                              width = 0.7, space = 0.15, ylim = c(0,7000), 
                              cex.axis = 0.7, las = 1,
                             col = c("#B72E56", "#61B94C", "#7006C2"), border = NA)
text(categoryCountPlot, categoryCount, 
     labels = categoryCount, col = "white", pos = 1, cex= 0.8)
```


```{r}
# Plot: Profit distribution
par(mar=c(5,8,4,2))
lossOutlier = which(superstore_2011_2015$Profit < 1.7280 | superstore_2011_2015$Profit > 70.7220)
lossOutlierData <- superstore_2011_2015[-lossOutlier,]
hist(lossOutlierData$Profit,
     breaks = 25,
     ylim = c(0,1000),
     main="Histogram of Profit earned",
     xlab = "Profit ($)",
     ylab = "Count",
     col = terrain.colors(10))
```


```{r}
par(mar=c(5,8,4,2))
# Plot: Scatter plot of Total Sales vs Profit vs Discount
plot_ly(x=superstore_2011_2015$Total_Sales, 
        y=superstore_2011_2015$Profit, 
        z=superstore_2011_2015$Discount, 
        type="scatter3d", mode="markers", color=superstore_2011_2015$Sales) %>%
  layout(scene = list(xaxis = list(title = "Sales"), 
                      yaxis = list(title = "Profit"), 
                      zaxis = list(title = "Discount Percentage")))
```


```{r out.width='\\textwidth',fig.align='center', fig.width=10}
# Plot 10: Time series analysis of Profit

# Typecasting to date
superstore_2011_2015$OrderDateColumn <- as.Date(superstore_2011_2015$`Order.Date`, "%m/%d/%Y")
superstore_2011_2015$OrderDateColumn <- format(as.Date(superstore_2011_2015$OrderDateColumn), "%Y-%m")

# Group by date and calculate Profit and Loss
timeSeriesProfitData <- aggregate(`Sales` ~ OrderDateColumn + Category, 
                                  data = superstore_2011_2015, FUN = sum, na.rm = TRUE)

ggplot(timeSeriesProfitData, aes(x = factor(OrderDateColumn), y = Sales, group = Category, color = Category)) +  
  geom_line(size = 1) +
  scale_color_manual(values=c("#FDC534", "#007FFE", "#D61E29")) +
  theme_gray() +
  labs(x="Date", y="Profit($)", 
       title = "Profit obtained for different product categories", 
       subtitle = "Dataset: Superstore Data") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 6)) +
  theme(axis.text.y = element_text(hjust=1, size = 14)) +
  theme(plot.title = element_text(size=12, hjust=0.5, colour="black", vjust=-1)) +
  theme(plot.subtitle = element_text(size=9, hjust=0.5, colour="black", vjust=-1))
```

<br><b><p>
<font size=5 color="#a84551">
Hypothesis Testing
</font>
</p></b>

<br><b><p>
<font size=4 color="#a84551">
1. Hypothesis:
</font>
</p></b>

<p>
<font size=3 color="#326ab4">
<b>Ho :</b> Average profit of the company in the US region is not $25 <br>
<b>Ha :</b> Average profit of the company in the US region is $25 <br>
</font>
</p>

```{r warning=FALSE}

#Ho : Average profit of the company in the US region is not $25 
#Ha : Average profit of the company in the US region is $25 

# t-test (One sample)

oneSampleData <- superstore_2011_2015[sample(nrow(superstore_2011_2015), 29), ]
t.test(oneSampleData$Profit, conf.level = .95, mu = 25)  
```

<br><b><p>
<font size=4 color="#a84551">
2. Hypothesis:
</font>
</p></b>
<p>
<font size=4 color="#326ab4">
<b>Ho :</b> True difference in average profit of Office Supplies and Technology is not 0   <br>
<b>Ha :</b> True difference in average profit of Office Supplies and Technology is  0 <br>
</font>
</p>

```{r warning=FALSE}

OfficeSuppliesProfit <- subset(superstore_2011_2015, Category =="Office Supplies") 
TechnologyProfit <- subset(superstore_2011_2015, Category =="Technology") 

OfficeSuppliesRandomSample <- OfficeSuppliesProfit[sample(nrow(OfficeSuppliesProfit), 25), ]
TechnologyRandomSample <- TechnologyProfit[sample(nrow(TechnologyProfit), 25), ]

t.test(OfficeSuppliesRandomSample$Profit, TechnologyRandomSample$Profit)
```

<br><b><p>
<font size=4 color="#a84551">
3. Hypothesis:
</font>
</p></b>
<p>
<font size=4 color="#326ab4">
<b>Ho :</b> True difference in average sales of West and East region is not 0    <br>
<b>Ha :</b> True difference in average sales of West and East region is  0    <br>
</font>
</p>

```{r warning=FALSE}
# t-test (Two sample)
westRegionSales <- subset(superstore_2011_2015, Region =="West") 
eastRegionSales <- subset(superstore_2011_2015, Region =="East") 

westRandomSample <- westRegionSales[sample(nrow(westRegionSales), 20), ]
eastRandomSample <- eastRegionSales[sample(nrow(eastRegionSales), 20), ]

t.test(westRandomSample$Sales, eastRandomSample$Sales, conf.level = 0.95) 
```

<br><b><p>
<font size=4 color="#a84551">
Data distribution of Shipping cost for Corporate vs Consumer segments
</font>
</p></b>
```{r warning=FALSE}

consumerShippingCost <- subset(superstore_2011_2015, Segment =="Consumer") 
corporateShippingCost <- subset(superstore_2011_2015, Segment =="Corporate") 


plotData <- subset(superstore_2011_2015, Segment =="Corporate" | Segment =="Consumer") 
ggplot(plotData, aes(x = plotData$Segment, y = plotData$Shipping.Cost, 
                                 color=plotData$Segment)) + 
  geom_jitter(position=position_jitter(0.2)) +
  theme_light() + 
  labs(y="Shipping costs ($)", x="Segments", title = "Shipping cost for Corporate vs Consumer segments", 
       subtitle = "Dataset: Superstore data") +
  theme(plot.title = element_text(size=14, hjust=0.5, colour="black", vjust=-1)) +
  theme(plot.subtitle = element_text(size=10, hjust=0.5, colour="black", vjust=-1)) + 
   scale_colour_manual(values = c("#4AB097", "#BB203C", "#FB761F")) +
  scale_shape_manual(values=c(1,17,19))
```

<br><b><p>
<font size=4 color="#a84551">
4. Hypothesis:
</font>
</p></b>
<p>
<font size=4 color="#326ab4">
<b>Ho :</b> True difference in average shipping cost of Consumer and Corporate segments is not 0<br>
<b>Ha :</b> True difference in average shipping cost of Consumer and Corporate segments is 0<br>
</font>
</p>

```{r}
# t-test (Two sample)
consumerRandomSample <- consumerShippingCost[sample(nrow(consumerShippingCost), 24), ]
corporateRandomSample <- corporateShippingCost[sample(nrow(corporateShippingCost), 24), ]

t.test(consumerRandomSample$Shipping.Cost, corporateRandomSample$Shipping.Cost, conf.level = 0.95) 
```


<br><b><p>
<font size=4 color="#a84551">
5. Hypothesis:
</font>
</p></b>
<p>
<font size=4 color="#326ab4">
<b>Ho :</b> Company's average sales is higher in the West region than East region of the US<br>
<b>Ha :</b> Company's average sales is higher in the East region than West region of the US<br>
</font>
</p>
```{r}
# t-test (Two sample)
t.test(westRandomSample$Sales, eastRandomSample$Sales, conf.level = 0.95,
       alternative = "greater") 
```

<br><b><p>
<font size=5 color="#a84551">
Correlation and Regression analysis
</font>
</p></b>

```{r}
# Correlation between Sale, Discount, Profit, Quantity and Shipping cost

corrData <- data.frame(Sales = superstore_2011_2015$Sales,
                       Discount = superstore_2011_2015$Discount,
                       Profit = superstore_2011_2015$Profit,
                       Quantity = superstore_2011_2015$Quantity,
                       `Shipping Cost` = superstore_2011_2015$Shipping.Cost)
ggcorrplot(cor(corrData), 
           hc.order = TRUE, 
           type = "lower", lab = TRUE, 
           insig = "blank",
           ggtheme = ggplot2::theme_grey(),
           title = "Correlation between Company's Sales stats")
```
```{r}
# Linear Regression Model
model2 <- lm(Shipping.Cost ~ Sales + Category, data = superstore_2011_2015)
summary(model2)
```

```{r}
# PLot1

p1 <- ggplot(superstore_2011_2015, aes(x = Sales, 
                             y = Shipping.Cost,
                             col = Profit)) + 
  xlim(c(0,7500)) + ylim(c(0,1000)) +
  geom_point() +
  theme_minimal() +
  theme(axis.text=element_text(size=12)) +
  geom_smooth(method="lm", formula = y~x, color = "red") +
  facet_grid(~Segment)
p1 + scale_color_gradient(low="pink", high="blue")
```

